comgen-outline

### 2017-12-18 paper/case1-generics.Rmd
switch out for prevalence label in case 1

Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions [@Prasada2013]: *majority characteristic* (e.g., "Ducks have wings."),  *minority characteristic* (e.g., "Robins lay eggs."), *striking* (e.g. "Mosquitos carry malaria."),  *false generalization* (e.g., "Robins are female."), and *absent features* (e.g. "Lions lay eggs.").
We further craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high feature-probabilities (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
This elicitation procedure includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

# d.gen.endorse.summary %>%
#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
generics.endorsement.spectrum <- left_join(
  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
) %>%
  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
  geom_linerange(position = position_dodge())+
  #geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
  guides(fill = guide_colorbar(title = 'feature probability',
                               ticks = F))+
  theme(legend.position = 'bottom')
  #geom_hline(yintercept = -0.25, lty = 3)+
  #geom_hline(yintercept = 0.25, lty = 3)
```

@@

In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
We next measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.

## Experiment 1b: Feature-probability prior elicitation

The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). Now, do you think it lays eggs? Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
].

This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").

@@

This whole procedure was repeated two times (two trials).
In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve).

@@

There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\  \@ref(fig:generic-endorsement-priors-figure) A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure \  \@ref(fig:simulations) A).
The property *being female* is present in almost all categories in almost exactly the same proportion, where as properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 feature-probability) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because the endorsement model makes different predictions depending on the shape of the prior.

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
We do this using a Bayesian mixture model, which assumes that the data generated for each property (e.g., \textsc{lay eggs}) comes from one of two underlying Beta distributions (*Mixture of Betas*).^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in feature-probability or prevalence values close to or equal to 0.
This "null distribution" is potentially present for all features in exactly the same way.
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix.

@@

The prior distributions over feature-probabilities are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs. blue lines). 
The *Single Beta* model does okay for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.

<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data. -->
<!-- Indeed, the data strongly suggests the feature-probability prior is structured. -->

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over feature-probabilities for eight properties. B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution. Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

@@

gen.priors.cdfs <-m.gen.endorse.priors.posteriorPredictive %>%
  mutate(src = factor(src, levels = c("Data", "Structured", "Unstructured"),
                      labels = c("Empirical distribution", 
                                 "Mixture of Betas",
                                 "Single Beta"))) %>%
ggplot(.,
           aes( x = prevalence, color = src, lty = src))+
    #geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("Feature-probability") +
    ylab("Cumulative probability density")+
    theme(legend.title = element_blank(), legend.position = 'bottom')

@@

To understand the generative process of generic endorsement, we articulate a set of formal models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
As the simplest baseline hypothesis, we first explore how well referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.

Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on feature-probabilities $P(h)$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category feature-probability (e.g, the prevalence of laying eggs among robins).
There are several substantive components to this hypothesis: (a) the prior distribution $P(h)$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs. not uttering it, and (c) the core semantics of a generalization is an uncertain threshold.
As a control model, we assign a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keep the prior and the decision-theoretic architecture in place. 
This provides a strict test of the uncertain-threshold hypothesis (c).

@@

#### Referent feature-probability

From the feature-probability prior data (Expt. 1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \  \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet). 
The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).

However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
This includes generics that are judged true with relatively low referent feature-probabilities (e.g., "Mosquitos carry malaria") and false with relatively high referent feature-probabilities (e.g., "Sharks don't eat people").

#### Cue validity and referent feature-probability

@@

As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* predict generic endorsementse.
If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
*Cue validity* thus captures the distinctiveness of the feature for the category. 
For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
In addition, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.

We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and can be derived via Bayes' Rule:
$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
Previous empirical studies of generic language, however, have not measured feature-probability priors and instead tried to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.

@@

A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (human endorsement both $> 0.9$).
Deviations, however, still remain.
For example, "Robins lay eggs" still receives only intermediate endorsement by this model (`r round(reg.robins.lay.eggs[[1,"prediction_mean"]], 2)` [`r round(reg.robins.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is judged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"high"]], 2)`]).

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of a simple model based on cue validity.
"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
Negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category (low cue validity), and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high (most mosquitos don't carry malaria).
A simple metric like cue validity is too blunt to capture these subtleties.

>>>>

Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions [@Prasada2013]: *majority characteristic* (e.g., "Ducks have wings."),  *minority characteristic* (e.g., "Robins lay eggs."), *striking* (e.g. "Mosquitos carry malaria."),  *false generalization* (e.g., "Robins are female."), and *absent features* (e.g. "Lions lay eggs.").
We further craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(h)$ (Expt. 1b).
This elicitation procedure includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

# d.gen.endorse.summary %>%
#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
generics.endorsement.spectrum <- left_join(
  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
) %>%
  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
  geom_linerange(position = position_dodge())+
  #geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
  guides(fill = guide_colorbar(title = 'Prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')
  #geom_hline(yintercept = -0.25, lty = 3)+
  #geom_hline(yintercept = 0.25, lty = 3)
```

@@

In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
We next measure the prevalence prior distribution and articulate a set of formal models that try to predict these endorsement data.

## Experiment 1b: Prevalence prior elicitation

The prevalence prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). Now, do you think it lays eggs? Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
].

This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(h \mid k)$.
We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").

@@

This whole procedure was repeated two times (two trials).
In total, each participant generated ten animal names and reported on the prevalence of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve).

@@

There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\  \@ref(fig:generic-endorsement-priors-figure) A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure \  \@ref(fig:simulations) A).
The property *being female* is present in almost all categories in almost exactly the same proportion, where as properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because the endorsement model makes different predictions depending on the shape of the prior.

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
We do this using a Bayesian mixture model, which assumes that the data generated for each property (e.g., \textsc{lay eggs}) comes from one of two underlying Beta distributions (*Mixture of Betas*).^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.
This "null distribution" is potentially present for all features in exactly the same way.
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix.

@@

The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs. blue lines). 
The *Single Beta* model does okay for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.

<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data. -->
<!-- Indeed, the data strongly suggests the prevalence prior is structured. -->

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties. B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution. Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

@@

gen.priors.cdfs <-m.gen.endorse.priors.posteriorPredictive %>%
  mutate(src = factor(src, levels = c("Data", "Structured", "Unstructured"),
                      labels = c("Empirical distribution", 
                                 "Mixture of Betas",
                                 "Single Beta"))) %>%
ggplot(.,
           aes( x = prevalence, color = src, lty = src))+
    #geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("prevalence") +
    ylab("Cumulative probability density")+
    theme(legend.title = element_blank(), legend.position = 'bottom')

@@

To understand the generative process of generic endorsement, we articulate a set of formal models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
As the simplest baseline hypothesis, we first explore how well referent-category prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
As a secondary alternative hypothesis, we explore whether referent prevalence and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.

Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(h)$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category prevalence (e.g, the prevalence of laying eggs among robins).
There are several substantive components to this hypothesis: (a) the prior distribution $P(h)$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs. not uttering it, and (c) the core semantics of a generalization is an uncertain threshold.
As a control model, we assign a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keep the prior and the decision-theoretic architecture in place. 
This provides a strict test of the uncertain-threshold hypothesis (c).

@@

#### Referent prevalence

From the prevalence prior data (Expt. 1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \  \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet). 
The referent prevalence baseline is a decent model of these data because our stimulus set includes generics that are true with high prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).

However, large deviations from an account based purely on referent prevalence remain: Generics in which the referent-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent prevalence ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
This includes generics that are judged true with relatively low referent prevalence (e.g., "Mosquitos carry malaria") and false with relatively high referent prevalence (e.g., "Sharks don't eat people").

#### Cue validity and referent prevalence

@@

As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* predict generic endorsementse.
If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
*Cue validity* thus captures the distinctiveness of the feature for the category. 
For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
In addition, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.

We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a prevalence given the kind $P(h \mid k)$.
If there is a finite number of kinds in the prevalence prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the prevalence prior and can be derived via Bayes' Rule:
$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
Previous empirical studies of generic language, however, have not measured prevalence priors and instead tried to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *prevalence prior derived cue validity*, see Appendix.

@@

A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (human endorsement both $> 0.9$).
Deviations, however, still remain.
For example, "Robins lay eggs" still receives only intermediate endorsement by this model (`r round(reg.robins.lay.eggs[[1,"prediction_mean"]], 2)` [`r round(reg.robins.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is judged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"high"]], 2)`]).

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of a simple model based on cue validity.
"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
Negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category (low cue validity), and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high (most mosquitos don't carry malaria).
A simple metric like cue validity is too blunt to capture these subtleties.
